---
title: "CS 329E Data Visualization - Tableau Project 2"
author: "Madeline Packard, Arthur DeVitalis"
date: "April 13, 2015"
output: html_document
---

This data was obtained by research conducted by the Brain and Gender Laboratory at Texas A&M University, under Gerianne Alexander, Ph.D.

In this research, participants agreed to complete a Pre-School Activities Iventory (PSAI). The PSAI is a psychometric scale used to assess gender role behavior in young children, and consists of 24 items that measure how frequently the participant played with certain toys (e.g., guns), engaged in specific activities (e.g., "playing house"), and displayed various characteristics (e.g., "enjoys rough and tumble play") when the participant was a pre-school-aged child. While typically used by parents to assess and describe the behavior of young children, the participants in this study were instructed to recall their preferences at a young age. Participants indicated how often they engaged in different types of play using a 5-point Likert scale ranging from 1 "never" to 5 "very often."

Participants were also asked to complete the Bem Sex Role Iventory (BSRI) - a measure of masculinity-femininity and gender roles and how people identify themselves. 

## The Data
```{r, include=FALSE, results = "hide"}
source("../01 SQL Crosstabs/packages.R", echo = FALSE)
```
```{r, message=FALSE}
source("../01 SQL Crosstabs/Crosstabs_Project2.R", echo = FALSE)
```

```{r, message=FALSE, echo = TRUE}
head(toys_df)
```

A high total score on the PSAI (PSAI_Total) indicates more masculine behavior and a lower total score indicates more feminine behavior.

The BEM variables (BEM masc, BEM fem) are additional measures for indentifying masculine and feminine traits.

The "MTOY" and "FTOY" variables refer to masculine toy preference and female toy preference, with a scale of 1 to 5.

For gender, 1 = Male; 2 = Female.

This dataframe also includes variables Latitude and Longitude, indicating the geographic location where the participants took the online study.

## Crosstabs

**Rank**


The first contigency table we created ranks by highest PSAI_Total score.

```{r, message=FALSE, echo = TRUE}
tbl_df(PSAIrank_df)
```

We created a second table where we selected occurances where gender was female, and ranked masculine behavior by age.

```{r, message=FALSE, echo = TRUE}
tbl_df(PSAIrank2_df)
```

**Nth Value**

We were interested in observing the maximum PSAI_Total score for each age when partitioned by gender.

```{r, message=FALSE, echo = TRUE}
tbl_df(PSAInthval_df)
```

**Max Value/ Last Value/ Difference**

We still need to make this table!

**Cumulative Distribution**

Finally, we considered looking at the cumulative distribution of the PSAI_Total scores, partitioned by age and ordered by gender.


```{r, message=FALSE, echo = TRUE}
tbl_df(PSAIcume_dist_df)
```
