---
title: "CS 329E Data Visualization - Tableau Project 2"
author: "Madeline Packard, Arthur DeVitalis"
date: "April 13, 2015"
output: html_document
---

This data was obtained by research conducted by the Brain and Gender Laboratory at Texas A&M University, under Gerianne Alexander, Ph.D.

In this research, participants agreed to complete a Pre-School Activities Iventory (PSAI). The PSAI is a psychometric scale used to assess gender role behavior in young children. A high total score on the PSAI indicates preference for male-typical toys (ie. trucks or guns), while a low total score indicates a preference for female-typical toys (ie. dolls or baking pans). Participants were also asked to complete the Bem Sex Role Iventory (BSRI) - a measure of masculinity-femininity and gender roles and how people identify themselves.


```{r, include=FALSE, results = "hide"}
source("../01 SQL Crosstabs/packages.R", echo = FALSE)
```
```{r, message=FALSE}
source("../01 SQL Crosstabs/Crosstabs_Project2.R", echo = TRUE)
```

```{r, message=FALSE, echo = FALSE}
head(toys_df)
```