---
title: "CS 329E Data Visualization - Tableau Project 2"
author: "Madeline Packard, Arthur DeVitalis"
date: "April 13, 2015"
output: html_document
---

This data was obtained by research conducted by the Brain and Gender Laboratory at Texas A&M University, under Gerianne Alexander, Ph.D.

In this research, participants agreed to complete a Pre-School Activities Iventory (PSAI). The PSAI is a psychometric scale used to assess gender role behavior in young children, and consists of 24 items that measure how frequently the participant played with certain toys (e.g., guns), engaged in specific activities (e.g., "playing house"), and displayed various characteristics (e.g., "enjoys rough and tumble play") when the participant was a pre-school-aged child. While typically used by parents to assess and describe the behavior of young children, the participants in this study were instructed to recall their preferences at a young age. Participants indicated how often they engaged in different types of play using a 5-point Likert scale ranging from 1 "never" to 5 "very often."

Participants were also asked to complete the Bem Sex Role Iventory (BSRI) - a measure of masculinity-femininity and gender roles and how people identify themselves. 

**The Dataframe**
```{r, include=FALSE, results = "hide"}
source("../01 SQL Crosstabs/packages.R", echo = FALSE)
```
```{r, message=FALSE}
source("../01 SQL Crosstabs/Crosstabs_Project2.R", echo = FALSE)
```

```{r, message=FALSE, echo = TRUE}
head(toys_df)
```

A high total score on the PSAI (PSAI_Total) indicates more masculine behavior and a lower total score indicates more feminine behavior.

The BEM variables (BEM masc, BEM fem) are additional measures for indentifying masculine and feminine traits.

The "MTOY" and "FTOY" variables refer to masculine toy preference and female toy preference, with a scale of 1 to 5.

This dataframe also includes variables Latitude and Longitude, indicating the geographic location where the participants took the online study.

**Crosstabs**

The first contigency table we created ranks the total PSAI scores by ascending order, partitioned by gender.

```{r, message=FALSE, echo = TRUE}
head(PSAIrank_df)
```